\section{Introduction}
\label{sec:introduction}
Investment has been seen as an important part of explaining the business cycle for a long time. It remains the most volatile variable in the macroeconomy. Over the past few decades, the role of investment in the business cycle has been continuously discussed, with new model environments being proposed \citep{greenwoodInvestmentCapacityUtilization1988,greenwoodLongRunImplicationsInvestmentSpecific1997a,fisherDynamicEffectsNeutral2006,justinianoInvestmentShocksBusiness2010,winberryLumpyInvestmentBusiness2021}.

Early research has drawn attention to the investment shock because of the obvious trend in the data on the relative price between investment goods and consumption goods, which implies another trend term in the investment specific technology besides the neutral technology \citep{greenwoodInvestmentCapacityUtilization1988}. After that, quantitative results have been established by \cite{greenwoodLongRunImplicationsInvestmentSpecific1997a} using a calibrated DSGE model, and by \cite{fisherDynamicEffectsNeutral2006} using a structural VAR model. Both of them claimed that the investment shock accounts for about half of the forecast error of the output and the working hours.

A new wave of research about the investment shock is stimulated by \cite{smetsShocksFrictionsUS2007}, who estimated a more frictional model based on \cite{christianoNominalRigiditiesDynamic2005} using Bayesian estimation. Using the same approach, \cite{justinianoInvestmentShocksBusiness2010, justinianoInvestmentShocksRelative2011} argued again that the investment shocks are the main source of the business cycle. While the investment shock shows strong effects on the macroeconomic variables, there are other candidates being proposed to account for the business cycle. \cite{christianoRiskShocks2014} and \cite{kamberFinancialFrictionsRole2015} argued that investment shock is less important once the model includes financial friction and shocks in the financial market.

Though I use the name of investment shock in the previous paragraphs, there are various kinds of specifications being discussed. Among them, the most classic one is the investment specific technology (IST) shock, which increases the technology level to produce investment goods from consumption goods \citep{greenwoodLongRunImplicationsInvestmentSpecific1997a, fisherDynamicEffectsNeutral2006, justinianoInvestmentShocksBusiness2010}. Besides, \cite{justinianoInvestmentShocksRelative2011, kamberFinancialFrictionsRole2015} distinguished the IST shock from the marginal efficiency of investment (MEI) shock, which represents the technology level to produce capital goods from investment goods. However, the difference between these two shocks relies on the detailed modeling of the capital production process. If the capital production is modelled by one capital law of motion equation, then those two shocks cannot be distinguished in their effect, and thus I make no clarification between them except for Section~\ref{sec:robustness:mei}. In addition, many works have discussed the IST news shock, in the sense that the shock is known by agents now but will affect the economy several periods later \citep{schmitt-groheWhatsNewsBusiness2012, benzeevInvestmentSpecificNewsShocks2015, liaoNewsShocksInvestmentspecific2023}. However, this kind of shock is beyond the scope of this paper.

Although the IST shock has been considered an important driving force of the business cycle, it fails to generate the comovement between consumption, investment and inflation. To solve the comovement problem, \cite{nireiOriginsPropagationAnimal} proposed an investment demand shock based on a model featuring firms' heterogeneity and the lumpy investment assumption \footnote{Due to lumpy investment, there is an inaction region of current capital in which firms will not invest. This region is determined by the production cost and the expected demand faced by the firm.

Suppose there are some high-productivity firms endowed with an idiosyncratic productivity shock. First, the production cost of these firms will decrease; thus other firms that use their products as intermediate materials enjoy a lower cost as well, and may increase production and investment. Second, those high-productivity firms may increase production themselves, which pushes up aggregate demand; thus other firms may enjoy higher demand for their products, and increase their investment as well.

In summary, through the supply channel and the demand channel, the idiosyncratic productivity shock propagates to the whole economy. For the propagation effect to be large enough, the friction of lumpy investment plays an important role. Because of this friction, firms nearly always invest a little more than their optimal investment, which can amplify an idiosyncratic shock into a macro-level shock.}. With the calibrated model, the investment demand shock generates the comovement between consumption and investment. While the shock is traced back to idiosyncratic productivity shocks, at the aggregate level it appears as a deviation of investment from the original investment decision made in a shock-free environment. Because of this, the investment demand shock can also be represented in a DSGE model without heterogeneity, and be estimated using the same approach as \cite{smetsShocksFrictionsUS2007}.

However, since this shock requires fixing the endogenous investment decision, the solution method of the rational expectation equilibrium needs to be separated into two steps. In the first step, the model includes all shocks and frictions except for the investment demand shock, from where the endogenous investment decision is solved. In the second step, the investment is decided by both the endogenous investment decision and the exogenous investment demand shock. It is worth pointing out that the endogenous investment decision cannot be changed in the second step, and thus investment demand is exogenously increased by the shock. Although the investment decision is fixed, households can still adjust their decisions on other terms, such as consumption and labor input, and thus the second step solves another equilibrium. This equilibrium, finally, will be used to compute the likelihood.

The identification strategy is not direct---it is hard to directly identify the investment demand shock from data, as the shock originates from idiosyncratic productivity shocks. Moreover, though we can use the relative price of investment goods as a proxy for the IST shock in some sense, there is still a concern that we might attribute all residuals to the investment demand shock. Therefore, I postpone this exercise to a later section and rely on the theoretical difference---whether the shock generates comovement between consumption, investment and inflation---to identify the two shocks in the baseline result. However, due to the high-dimensional parameter space, the comovement difference is hard to test across all combinations of parameter values. Therefore, I acknowledge the shortcoming of such an identification strategy.

Section~\ref{sec:model} introduces the baseline model. Section~\ref{sec:solution} presents the solution method and incorporates the investment demand shock. Section~\ref{sec:estimation} describes the Bayesian estimation, and Section~\ref{sec:results} reports the benchmark results. Section~\ref{sec:robustness} provides robustness checks, and Section~\ref{sec:conclusion} concludes.